### 2018-01-29 submission/manuscript.Rmd
nick suggestions results

@@

***The Number of OTUs is Dependent on HiFi DNA Polymerase Used:***
After normalization by individual, for each cycle number, we observed that for fecal samples the number of OTUs identified was dependent upon the HiFi DNA polymerase used and this difference increased as the depth of sub-sampling increased [Figure 1]. Lower cycle numbers (15-20) resulted in less differences between HiFI DNA polymerase while cycle numbers of 25, 30, and 35 had larger clearer defined differences [Figure 1]. Only 35 cycles had HiFi DNA polymerase differences that were significantly different at all sub-sampling levels (P-value `r ifelse(max(filter(fs_anova_summary, cycle == "35x")[, "bh"]) < 0.0001, invisible("<"), invisible("check data"))` 0.0001) [Table S1]. At sub-sampling depth of 5000 or higher 25 and 30 cycles had HiFi DNA polymerase differences (P-value `r ifelse(max(filter(fs_anova_summary, cycle == "30x", sub_sample_level != 1000)[, "bh"]) < 0.05 & max(filter(fs_anova_summary, cycle == "25x", sub_sample_level != 1000)[, "bh"]) < 0.05, invisible("<"), invisible("check data"))` 0.05) [Table S1]. Using a Tukey post-hoc test only at 35 cycles were significant differences found to be mainly driven by Platinum being different than all other DNA polymerases across sub-sampling depth (P-value `r ifelse(max(filter(fs_tukey_summary, padj < 0.05)[, "padj"]) < 0.05,  invisible("<"), invisible("check data"))` 0.05) [Table S2].

This HiFi DNA polymerase dependent difference in the number of OTUs was also observed in the mock community samples with the same DNA polymerases being high (Platinum) and low (Accuprime) respectively [Figure 2 & Table S3]. Conversely, differences between HiFi DNA polymerase were observed as early as 20 cycles and a sub-sampling depth of 1000 sequences (P-value = `r format(filter(mock_anova_summary, sub_sample_level == 1000, cycle == "20x")[, "bh"], digits = 1, nsmall = 1)`) [Table S3]. Using a Tukey post-hoc test differences between Platinum and the other HiFi DNA polymerases was the major driver of the differences seen at different cycle numbers and sub-sampling depths [Table S4]. Both fecal and mock samples consistently showed that across sub-sampling depth and cycle number the lowest number of OTUs identified was from Accuprime^TM^ while the highest was from Platinum for both fecal and mock samples [Figure 1 & 2].

***Minimal Bray-Curtis Differences are Detected by Cycle Number:***
Overall, there was very little difference between each respective 5-cycle increment (e.g. 15x vs 20x) for both fecal and mock samples and this was consistent across the different sub-samplings used [Figure 3]. Two exceptions to the low differences between 5-cycle increments can be found. The first, that there seems to be large differences for fecal samples between 20x vs. 25x that is robust against sub-sampling depth [Figure 3A-B]. Second, for the mocks, where data is available, there appears to be a similar large difference detected between 20x and 25x [Figure 3D]. Regardless, by the time PCR cycles reach 25x there does not seem to be large differences in the community between the same sample [Figure 3].

Using PERMANOVA to test whether there were any differences within HiFi DNA polymerase groups based on cycle number, only Phusion had cycle dependent differences at 1000 and 5000 sub-sampling depth (P-value = `r format(filter(bray_permanova_by_taq_results, sub_sample_level == 1000, taq == "PHU")[, "bh"], digits = 1, nsmall = 1)` and `r format(filter(bray_permanova_by_taq_results, sub_sample_level == 5000, taq == "PHU")[, "bh"], digits = 1, nsmall = 1)`, respectively). Interestingly, Phusion was one of only two DNA polymerase that managed to have samples for the 1000 sub-sampling depth at 15 cycles. Next, we assessed whether there were any major differences between 5 cycle increments within each sample. We found that there was no detectable difference in Bray-Curits index when comparing to the previous 5 cycle increment (P-value `r ifelse(min(bray_sim_to_prev_cycle_kruskal_results$bh, na.rm = T) > 0.05, invisible(">"), invisible("check data"))` 0.05). However, Phusion at 1000 sub-sampling depth had a P-value = `r format(filter(bray_sim_to_prev_cycle_kruskal_results, sub_sample_level == 1000, taq == "PHU")[, "pvalue"], digits = 1, nsmall = 1)` before multiple comparison correction. It should be noted that at higher sub-sampling depths these differences in Bray-Curits indicies disappear for both differences in cycle number and within 5 cycle increments within an individual.

***Sequence Error is Dependent on both HiFi DNA Polymerase and Cycle Number Used:***
Differences by HiFi DNA polymerase in the median average per base error varied without a clear pattern across sub-sampling depth [Table S5]. Generally, the highest values were for the Kappa HiFI DNA polymerase and the pre-cluster step and chimera removal by VSEARCH had little effect on this rate [Figure 4]. Generally, there were small differences between the various HiFi DNA polymerase at lower cycle numbers and larger differences at higher cycle number with Platinum having large differences between all other HiFi DNA polymerase [Figure 4B-C and Table S6].

@@

***Chimeric Sequences Correlate with OTUs and are HiFi DNA Polymerase Dependent:***
After chimera removal using VSEARCH and removal of sequences that did not classify as bacteria we assessed the percentage of sequences that were still chimeric within our mock community. At all levels of sub-sampling and cycle number there were significant differences between the HiFi DNA polymerase used (P-value `r ifelse(max(filter(kruskal_chimera_prev, sub_sample_level > 500)[, "bh"]) < 0.05, invisible("<"), invisible("check data"))` 0.05) [Table S9]. Using a Dunn's post-hoc test the vast majority of these differences were driven by Platinum being different then all other HiFi DNA polymerase across cycle number and sub-sampling depth [Table S10]. Generally, across sub-sampling depth and cycle number Accuprime^TM^ had the lowest chimera prevalence of all the HiFi DNA Polymerase regardless of whether pre.cluster or VSEARCH had been used [Figure 5].

For all DNA polymerase, a positive correlation was observed between chimeric sequences and number of OTUs, with this correlation being strongest for Accuprime, Platinum and Phusion HiFi DNA Polymerase [Figure 6]. In general, the R^2^ value between the number of OTUs and chimeric sequences did not change from the use of pre.cluster and VSEARCH [Figure 6]. Taken together this data suggests that a strong correlation exists between the number of OTUs and the prevalence of chimeric sequences. Additionally, Kappa had the highest per base error rate and the lowest correlations between the number of OTUs and chimeric sequences across sub-sampling depth [Figure 4 & 6].

>>>>

# Vector of sub samples used
sub_sample_level <- c("1000", "5000", "10000")

dist_data <- sapply(sub_sample_level, 
                    function(x) as.data.frame(read_csv(paste("../data/process/tables/bray_5_cycle_dist_",                                                x, "_data.csv", sep = ""))), simplify = F)

mock_dist_data <- sapply(sub_sample_level, 
                    function(x) as.data.frame(read_csv(paste("../data/process/tables/mock_bray_5_cycle_dist_", 
                                               x, "_data.csv", sep = ""))), simplify = F)

@@

***Number of OTUs is Dependent on the HiFi DNA Polymerase Used:***
In order to compare the number of OTUs across individuals a Z-score normalization by individual, by cycle number, was employed on the number of OTUs data. After normalization, we identified that there was a HiFi DNA polymerase dependent difference that became more apparent as the depth of sub-sampling increased [Figure 1]. Lower cycle numbers (15-20) resulted in less differences between HiFI DNA polymerase while cycle numbers of 25, 30, and 35 having distinct differences [Figure 1]. All subsampling levels were significantly different only at 35 cycles (P-value `r ifelse(max(filter(fs_anova_summary, cycle == "35x")[, "bh"]) < 0.0001, invisible("<"), invisible("check data"))` 0.0001) [Table S1]. There were differences in HiFi DNA polymerase at 25 and 30 cycles but the sub-sampling depth had to be 5000 or higher (P-value `r ifelse(max(filter(fs_anova_summary, cycle == "30x", sub_sample_level != 1000)[, "bh"]) < 0.05 & max(filter(fs_anova_summary, cycle == "25x", sub_sample_level != 1000)[, "bh"]) < 0.05, invisible("<"), invisible("check data"))` 0.05) [Table S1]. Platinum HiFi DNA polymerase was the main driver of the differences observed across all sub-sampling depths at 35 cycles, based on a Tukey post-hoc test (P-value `r ifelse(max(filter(fs_tukey_summary, padj < 0.05)[, "padj"]) < 0.05,  invisible("<"), invisible("check data"))` 0.05) [Table S2].

This HiFi DNA polymerase dependent difference in the number of OTUs was also observed in the mock community samples with the same DNA polymerases having high (Platinum) and low (Accuprime) number of OTUs [Figure 2 & Table S3]. Conversely, differences between HiFi DNA polymerase were observed as early as 20 cycles and a sub-sampling depth of 1000 sequences (P-value = `r format(filter(mock_anova_summary, sub_sample_level == 1000, cycle == "20x")[, "bh"], digits = 1, nsmall = 1)`) [Table S3]. Using a Tukey post-hoc test differences between Platinum and the other HiFi DNA polymerases was the major driver of the differences seen at different cycle numbers and sub-sampling depths [Table S4]. Both fecal and mock samples consistently showed that across sub-sampling depth and cycle number the lowest number of OTUs identified was from Accuprime^TM^ while the highest was from Platinum for both fecal and mock samples [Figure 1 & 2].

***Minimal Bray-Curtis Differences are Detected by Cycle Number:***
Overall, there was very little difference between each respective 5-cycle increment (e.g. 15x vs 20x) for both fecal and mock samples and this was consistent across the different sub-samplings used [Figure 3]. There were only two differences between 5-cycle increments that were identified. First, there were differences for the same fecal sample between 20x vs. 25x that was independent of HiFi DNA polymerase but dependent on sub-sampling depth (subsampled to 1000 = `r round(median(filter(dist_data[["1000"]], cycle_compare == "20to25")[, "distance"]), digits = 2)` (`r round(quantile(filter(dist_data[["1000"]], cycle_compare == "20to25")[, "distance"])["25%"], digits = 2)` - `r round(quantile(filter(dist_data[["1000"]], cycle_compare == "20to25")[, "distance"])["75%"], digits = 2)`) (median (25% - 75% quantile)), subsampled to 5000 = `r round(median(filter(dist_data[["5000"]], cycle_compare == "20to25")[, "distance"]), digits = 2)` (`r round(quantile(filter(dist_data[["5000"]], cycle_compare == "20to25")[, "distance"])["25%"], digits = 2)` - `r round(quantile(filter(dist_data[["5000"]], cycle_compare == "20to25")[, "distance"])["75%"], digits = 2)`), subsampled to 10000 = `r round(median(filter(dist_data[["10000"]], cycle_compare == "20to25")[, "distance"]), digits = 2)` (`r round(quantile(filter(dist_data[["10000"]], cycle_compare == "20to25")[, "distance"])["25%"], digits = 2)` - `r round(quantile(filter(dist_data[["10000"]], cycle_compare == "20to25")[, "distance"])["75%"], digits = 2)`)) [Figure 3A-B]. Second, for the mocks, where data is available, there were larger difference between 20x and 25x (subsampled to 1000 = `r round(median(filter(mock_dist_data[["1000"]], cycle_compare == "20to25")[, "distance"]), digits = 2)` (`r round(quantile(filter(mock_dist_data[["1000"]], cycle_compare == "20to25")[, "distance"])["25%"], digits = 2)` - `r round(quantile(filter(mock_dist_data[["1000"]], cycle_compare == "20to25")[, "distance"])["75%"], digits = 2)`)) [Figure 3D]. However, these differences between the next 5 cycle increment do not persist once 25 cylces are reached [Figure 3].

Using PERMANOVA to test for differences within HiFi DNA polymerase groups based on cycle number, only Phusion had cycle dependent differences at 1000 and 5000 sub-sampling depth (P-value = `r format(filter(bray_permanova_by_taq_results, sub_sample_level == 1000, taq == "PHU")[, "bh"], digits = 1, nsmall = 1)` and `r format(filter(bray_permanova_by_taq_results, sub_sample_level == 5000, taq == "PHU")[, "bh"], digits = 1, nsmall = 1)`, respectively). Phusion was one of only two HiFi DNA polymerases that managed to have samples for the 1000 sub-sampling depth at 15 cycles. Next, we assessed whether there were any major differences between 5 cycle increments within each sample. We found that there was no detectable difference in Bray-Curits index when comparing to the previous 5 cycle increment (P-value `r ifelse(min(bray_sim_to_prev_cycle_kruskal_results$bh, na.rm = T) > 0.05, invisible(">"), invisible("check data"))` 0.05). However, Phusion at 1000 sub-sampling depth had a P-value = `r format(filter(bray_sim_to_prev_cycle_kruskal_results, sub_sample_level == 1000, taq == "PHU")[, "pvalue"], digits = 1, nsmall = 1)` before multiple comparison correction. It should be noted that at higher sub-sampling depths these differences in Bray-Curits indicies disappear for both differences in cycle number and within 5 cycle increments within an individual.

***Sequence Error is Dependent on both HiFi DNA Polymerase and Cycle Number:***
Differences by HiFi DNA polymerase in the median average per base error varied without a clear pattern across sub-sampling depth [Table S5]. Generally, the highest per base median average error rates were for the Kappa HiFI DNA polymerase [Figure 4]. This error rate was minimally affected by both the pre-cluster step and chimera removal by VSEARCH [Figure 4]. There were small differences in the per base error rate between the various HiFi DNA polymerase at lower cycle numbers and larger differences at higher cycle number with Platinum having the largest differences of all the HiFi DNA polymerase [Figure 4B-C and Table S6].

@@

***Chimeric Sequences Correlate with OTUs and are HiFi DNA Polymerase Dependent:***
After chimera removal using VSEARCH and removal of sequences that did not classify as bacteria we assessed the percentage of sequences that were still chimeric within our mock community. At all levels of sub-sampling and cycle number there were significant differences between the HiFi DNA polymerase used (P-value `r ifelse(max(filter(kruskal_chimera_prev, sub_sample_level > 500)[, "bh"]) < 0.05, invisible("<"), invisible("check data"))` 0.05) [Table S9]. Differences between Platinum and all other HiFi DNA polymerases accounted for the vast majority of these differences independent of cycle number and sub-sampling depth when using a Dunn's post-hoc test [Table S10]. Generally, across sub-sampling depth and cycle number Accuprime^TM^ had the lowest chimera prevalence of all the HiFi DNA Polymerases regardless of whether pre.cluster or VSEARCH had been used [Figure 5].

For all DNA polymerase, a positive correlation was observed between chimeric sequences and number of OTUs, with this correlation being strongest for Accuprime, Platinum and Phusion HiFi DNA Polymerase [Figure 6]. In general, the R^2^ value between the number of OTUs and chimeric sequences did not change from the use of pre.cluster and VSEARCH [Figure 6]. Taken together, this data suggests that a strong correlation exists between the number of OTUs and the prevalence of chimeric sequences.

### 2018-01-29 submission/manuscript.tex
nick suggestions results

\textbf{\emph{The Number of OTUs is Dependent on HiFi DNA Polymerase
Used:}} After normalization by individual, for each cycle number, we
observed that for fecal samples the number of OTUs identified was
dependent upon the HiFi DNA polymerase used and this difference
increased as the depth of sub-sampling increased {[}Figure 1{]}. Lower
cycle numbers (15-20) resulted in less differences between HiFI DNA
polymerase while cycle numbers of 25, 30, and 35 had larger clearer
defined differences {[}Figure 1{]}. Only 35 cycles had HiFi DNA
polymerase differences that were significantly different at all
sub-sampling levels (P-value \textless{} 0.0001) {[}Table S1{]}. At
sub-sampling depth of 5000 or higher 25 and 30 cycles had HiFi DNA
polymerase differences (P-value \textless{} 0.05) {[}Table S1{]}. Using
a Tukey post-hoc test only at 35 cycles were significant differences
found to be mainly driven by Platinum being different than all other DNA
polymerases across sub-sampling depth (P-value \textless{} 0.05)
{[}Table S2{]}.

This HiFi DNA polymerase dependent difference in the number of OTUs was
also observed in the mock community samples with the same DNA
polymerases being high (Platinum) and low (Accuprime) respectively
{[}Figure 2 \& Table S3{]}. Conversely, differences between HiFi DNA
polymerase were observed as early as 20 cycles and a sub-sampling depth
of 1000 sequences (P-value = 0.002) {[}Table S3{]}. Using a Tukey
post-hoc test differences between Platinum and the other HiFi DNA
polymerases was the major driver of the differences seen at different
cycle numbers and sub-sampling depths {[}Table S4{]}. Both fecal and
mock samples consistently showed that across sub-sampling depth and
cycle number the lowest number of OTUs identified was from
Accuprime\textsuperscript{TM} while the highest was from Platinum for
both fecal and mock samples {[}Figure 1 \& 2{]}.

\textbf{\emph{Minimal Bray-Curtis Differences are Detected by Cycle
Number:}} Overall, there was very little difference between each
respective 5-cycle increment (e.g.~15x vs 20x) for both fecal and mock
samples and this was consistent across the different sub-samplings used
{[}Figure 3{]}. Two exceptions to the low differences between 5-cycle
increments can be found. The first, that there seems to be large
differences for fecal samples between 20x vs.~25x that is robust against
sub-sampling depth {[}Figure 3A-B{]}. Second, for the mocks, where data
is available, there appears to be a similar large difference detected
between 20x and 25x {[}Figure 3D{]}. Regardless, by the time PCR cycles
reach 25x there does not seem to be large differences in the community
between the same sample {[}Figure 3{]}.

Using PERMANOVA to test whether there were any differences within HiFi
DNA polymerase groups based on cycle number, only Phusion had cycle
dependent differences at 1000 and 5000 sub-sampling depth (P-value =
0.03 and 0.01, respectively). Interestingly, Phusion was one of only two
DNA polymerase that managed to have samples for the 1000 sub-sampling
depth at 15 cycles. Next, we assessed whether there were any major
differences between 5 cycle increments within each sample. We found that
there was no detectable difference in Bray-Curits index when comparing
to the previous 5 cycle increment (P-value \textgreater{} 0.05).
However, Phusion at 1000 sub-sampling depth had a P-value = 0.02 before
multiple comparison correction. It should be noted that at higher
sub-sampling depths these differences in Bray-Curits indicies disappear
for both differences in cycle number and within 5 cycle increments
within an individual.

\textbf{\emph{Sequence Error is Dependent on both HiFi DNA Polymerase
and Cycle Number Used:}} Differences by HiFi DNA polymerase in the
median average per base error varied without a clear pattern across
sub-sampling depth {[}Table S5{]}. Generally, the highest values were
for the Kappa HiFI DNA polymerase and the pre-cluster step and chimera
removal by VSEARCH had little effect on this rate {[}Figure 4{]}.
Generally, there were small differences between the various HiFi DNA
polymerase at lower cycle numbers and larger differences at higher cycle
number with Platinum having large differences between all other HiFi DNA
polymerase {[}Figure 4B-C and Table S6{]}.

@@

\textbf{\emph{Chimeric Sequences Correlate with OTUs and are HiFi DNA
Polymerase Dependent:}} After chimera removal using VSEARCH and removal
of sequences that did not classify as bacteria we assessed the
percentage of sequences that were still chimeric within our mock
community. At all levels of sub-sampling and cycle number there were
significant differences between the HiFi DNA polymerase used (P-value
\textless{} 0.05) {[}Table S9{]}. Using a Dunn's post-hoc test the vast
majority of these differences were driven by Platinum being different
then all other HiFi DNA polymerase across cycle number and sub-sampling
depth {[}Table S10{]}. Generally, across sub-sampling depth and cycle
number Accuprime\textsuperscript{TM} had the lowest chimera prevalence
of all the HiFi DNA Polymerase regardless of whether pre.cluster or
VSEARCH had been used {[}Figure 5{]}.

For all DNA polymerase, a positive correlation was observed between
chimeric sequences and number of OTUs, with this correlation being
strongest for Accuprime, Platinum and Phusion HiFi DNA Polymerase
{[}Figure 6{]}. In general, the R\textsuperscript{2} value between the
number of OTUs and chimeric sequences did not change from the use of
pre.cluster and VSEARCH {[}Figure 6{]}. Taken together this data
suggests that a strong correlation exists between the number of OTUs and
the prevalence of chimeric sequences. Additionally, Kappa had the
highest per base error rate and the lowest correlations between the
number of OTUs and chimeric sequences across sub-sampling depth
{[}Figure 4 \& 6{]}.

>>>>

\textbf{\emph{Number of OTUs is Dependent on the HiFi DNA Polymerase
Used:}} In order to compare the number of OTUs across individuals a
Z-score normalization by individual, by cycle number, was employed on
the number of OTUs data. After normalization, we identified that there
was a HiFi DNA polymerase dependent difference that became more apparent
as the depth of sub-sampling increased {[}Figure 1{]}. Lower cycle
numbers (15-20) resulted in less differences between HiFI DNA polymerase
while cycle numbers of 25, 30, and 35 having distinct differences
{[}Figure 1{]}. All subsampling levels were significantly different only
at 35 cycles (P-value \textless{} 0.0001) {[}Table S1{]}. There were
differences in HiFi DNA polymerase at 25 and 30 cycles but the
sub-sampling depth had to be 5000 or higher (P-value \textless{} 0.05)
{[}Table S1{]}. Platinum HiFi DNA polymerase was the main driver of the
differences observed across all sub-sampling depths at 35 cycles, based
on a Tukey post-hoc test (P-value \textless{} 0.05) {[}Table S2{]}.

This HiFi DNA polymerase dependent difference in the number of OTUs was
also observed in the mock community samples with the same DNA
polymerases having high (Platinum) and low (Accuprime) number of OTUs
{[}Figure 2 \& Table S3{]}. Conversely, differences between HiFi DNA
polymerase were observed as early as 20 cycles and a sub-sampling depth
of 1000 sequences (P-value = 0.002) {[}Table S3{]}. Using a Tukey
post-hoc test differences between Platinum and the other HiFi DNA
polymerases was the major driver of the differences seen at different
cycle numbers and sub-sampling depths {[}Table S4{]}. Both fecal and
mock samples consistently showed that across sub-sampling depth and
cycle number the lowest number of OTUs identified was from
Accuprime\textsuperscript{TM} while the highest was from Platinum for
both fecal and mock samples {[}Figure 1 \& 2{]}.

\textbf{\emph{Minimal Bray-Curtis Differences are Detected by Cycle
Number:}} Overall, there was very little difference between each
respective 5-cycle increment (e.g.~15x vs 20x) for both fecal and mock
samples and this was consistent across the different sub-samplings used
{[}Figure 3{]}. There were only two differences between 5-cycle
increments that were identified. First, there were differences for the
same fecal sample between 20x vs.~25x that was independent of HiFi DNA
polymerase but dependent on sub-sampling depth (subsampled to 1000 =
0.51 (0.4 - 0.79) (median (25\% - 75\% quantile)), subsampled to 5000 =
0.43 (0.33 - 0.63), subsampled to 10000 = 0.4 (0.24 - 0.43)) {[}Figure
3A-B{]}. Second, for the mocks, where data is available, there were
larger difference between 20x and 25x (subsampled to 1000 = 0.88 (0.42 -
0.91)) {[}Figure 3D{]}. However, these differences between the next 5
cycle increment do not persist once 25 cylces are reached {[}Figure
3{]}.

Using PERMANOVA to test for differences within HiFi DNA polymerase
groups based on cycle number, only Phusion had cycle dependent
differences at 1000 and 5000 sub-sampling depth (P-value = 0.03 and
0.01, respectively). Phusion was one of only two HiFi DNA polymerases
that managed to have samples for the 1000 sub-sampling depth at 15
cycles. Next, we assessed whether there were any major differences
between 5 cycle increments within each sample. We found that there was
no detectable difference in Bray-Curits index when comparing to the
previous 5 cycle increment (P-value \textgreater{} 0.05). However,
Phusion at 1000 sub-sampling depth had a P-value = 0.02 before multiple
comparison correction. It should be noted that at higher sub-sampling
depths these differences in Bray-Curits indicies disappear for both
differences in cycle number and within 5 cycle increments within an
individual.

\textbf{\emph{Sequence Error is Dependent on both HiFi DNA Polymerase
and Cycle Number:}} Differences by HiFi DNA polymerase in the median
average per base error varied without a clear pattern across
sub-sampling depth {[}Table S5{]}. Generally, the highest per base
median average error rates were for the Kappa HiFI DNA polymerase
{[}Figure 4{]}. This error rate was minimally affected by both the
pre-cluster step and chimera removal by VSEARCH {[}Figure 4{]}. There
were small differences in the per base error rate between the various
HiFi DNA polymerase at lower cycle numbers and larger differences at
higher cycle number with Platinum having the largest differences of all
the HiFi DNA polymerase {[}Figure 4B-C and Table S6{]}.

@@

\textbf{\emph{Chimeric Sequences Correlate with OTUs and are HiFi DNA
Polymerase Dependent:}} After chimera removal using VSEARCH and removal
of sequences that did not classify as bacteria we assessed the
percentage of sequences that were still chimeric within our mock
community. At all levels of sub-sampling and cycle number there were
significant differences between the HiFi DNA polymerase used (P-value
\textless{} 0.05) {[}Table S9{]}. Differences between Platinum and all
other HiFi DNA polymerases accounted for the vast majority of these
differences independent of cycle number and sub-sampling depth when
using a Dunn's post-hoc test {[}Table S10{]}. Generally, across
sub-sampling depth and cycle number Accuprime\textsuperscript{TM} had
the lowest chimera prevalence of all the HiFi DNA Polymerases regardless
of whether pre.cluster or VSEARCH had been used {[}Figure 5{]}.

For all DNA polymerase, a positive correlation was observed between
chimeric sequences and number of OTUs, with this correlation being
strongest for Accuprime, Platinum and Phusion HiFi DNA Polymerase
{[}Figure 6{]}. In general, the R\textsuperscript{2} value between the
number of OTUs and chimeric sequences did not change from the use of
pre.cluster and VSEARCH {[}Figure 6{]}. Taken together, this data
suggests that a strong correlation exists between the number of OTUs and
the prevalence of chimeric sequences.
